Biden to win the popular vote in the 2020 American presidential elections

### 2020-11-03 outputs/paper/paper.Rmd
Updated plots and report

>>>>

```{r, figures-side-age, fig.show="hold", out.width="50%", include = TRUE, echo = FALSE}
knitr::include_graphics(here::here("outputs/figures/ACS_age_distribution.pdf"))
knitr::include_graphics(here::here("outputs/figures/UCLA_age_distribution.pdf"))
```

```{r, figures-side-emp, fig.show="hold", out.width="50%", include = TRUE, echo = FALSE}
knitr::include_graphics(here::here("outputs/figures/ACS_employment_distribution.pdf"))
knitr::include_graphics(here::here("outputs/figures/UCLA_employment_distribution.pdf"))
```

```{r, figures-side-gender, fig.show="hold", out.width="50%", include = TRUE, echo = FALSE}
knitr::include_graphics(here::here("outputs/figures/ACS_gender_distribution.pdf"))
knitr::include_graphics(here::here("outputs/figures/UCLA_gender_distribution.pdf"))
```

```{r, figures-side-race, fig.show="hold", out.width="50%", include = TRUE, echo = FALSE}
knitr::include_graphics(here::here("outputs/figures/ACS_race_distribution.pdf"))
knitr::include_graphics(here::here("outputs/figures/UCLA_race_distribution.pdf"))
```
